---
title: "Something like Martin et al. 2015 in Stan"
author: ""
date: "10/4/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstan)
library(tidyverse)

# These lines allow for parallel chains in the Hamiltonian Monte Carlo steps.
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

## Reformat data for Stan

The first thing we have to do is put the simulated data in a format Stan can read.  Stan requires data in lists, so we have to do the following manipulation. Note each of the objects in the list correspond to a data element defined in the stan programs.

```{r}
source("data_sim.R")
dat_stan <- list(N = length(dat$year),
                 sets = dat$sets,
                 inter = dat$inter,
                 mort = dat$mort)
```

## Estimate the Poisson model for bycatch interactions

First, we'll estimate the rate of interaction per set using the Poisson model specification.

```{r, echo = T, results = 'hide'}
pois_fit <- stan(file = "poisson_model.stan", 
                 data = dat_stan, 
                 iter = 1000, 
                 chains = 4,
                 seed = 1234)
```

Now, lets check out the fit parameter to see if it comes close to what we know as the true rate parameter of 0.002.
```{r}
print(pois_fit)
plot(pois_fit)
```

Alhtough we can't see the parameter estimate because it's being masked by 0 because of rounding, the Rhat close to 1 indicates we got model convergence.  In the plot of the parameter we can see the posterior distribution for eta.  Looks pretty good!

## Estimate the binomial model for mortality resulting from bycatch interaction
```{r, echo = T, results = 'hide'}
binom_fit <- stan(file = "binomial_model.stan", 
                 data = dat_stan, 
                 iter = 1000, 
                 chains = 4,
                 seed = 1234)
```

```{r}
print(binom_fit)
plot(binom_fit)
```

Again, given we only have 20 observations to estimate the model with, this looks pretty good to the known true value.

